### 2018-03-08 paper/background.tex
Minor revision

@@

\noindent
The above makefile lists three tasks: (i) compile a utility library comprising
files \cmd{util.h} and \cmd{util.c} into \cmd{main.o} by executing the command
\cmd{gcc -c util.c}, (ii) compile the main source file \cmd{main.c} into
\cmd{main.o}, and (iii) link object files \cmd{util.o} and \cmd{main.o} into the
executable \cmd{main.exe}. The makefile contains the complete information about
the task \emph{dependency graph}, which is shown in Fig.~\ref{fig-make}(a).

@@

\Excel

>>>>

\subsection{The venerable \Make}

@@

\noindent
The above makefile lists three tasks: (i) compile a utility library comprising
files \cmd{util.h} and \cmd{util.c} into \cmd{main.o} by
executing\footnote{In this example we treat \cmd{gcc} as a pure function for the
sake of simplicity. In reality there are multiple versions of \cmd{gcc} and the
actual binary that is used to compile and link files is also listed as a task
dependency.} the command \cmd{gcc -c util.c}, (ii) compile the main source file
\cmd{main.c} into \cmd{main.o}, and (iii) link object files \cmd{util.o} and
\cmd{main.o} into the executable \cmd{main.exe}. The makefile contains the
complete information about the task \emph{dependency graph}, which is shown in
Fig.~\ref{fig-make}(a).

@@

\subsection{\Excel: a build system in disguise}

### 2018-03-08 paper/engineering.tex
Add iterative computations
Minor revision

\begin{itemize}
    \item Sandboxing
    \item Non-determinism, specifically, it's useless form. This doesn't
          include \Excel's \textsf{RANDBETWEEN} function, which is useful.
          To define correctness of non-deterministic build systems, one needs to
          switch from \hs{Applicative} and \hs{Monad} abstractions to
          \hs{Alternative} and \hs{MonadPlus}, respectively, but this is not
          required for actual implementations, most of which can happily accept
          non-deterministic results (with a notable exception of \Buck).
    \item Concurrency
    \item Cloud
\end{itemize}

>>>>

Or ``Build systems in the real world'', or ``Crazy things section''...

\begin{itemize}
    \item Sandboxing
    \item Non-determinism, specifically, its useless form. This doesn't
          include \Excel's \textsf{RANDBETWEEN} function, which is useful.
          To define correctness of non-deterministic build systems, one needs to
          switch from \hs{Applicative} and \hs{Monad} abstractions to
          \hs{Alternative} and \hs{MonadPlus}, respectively, but this is not
          required for actual implementations, most of which can happily accept
          non-deterministic results (with a notable exception of \Buck).
    \item Concurrency: nothing fundamentally difficult and fits our theory, but
          hard to get right in practice.
    \item Cloud aspects: eviction/garbage collection, `frankenbuilds', etc.
    \item Iterative computations, e.g. LaTeX.
    \item Polymorphic keys and values: tasks with multiple outputs, e.g. GHC's
          \cmd{hi} and \cmd{o} files, phony tasks, etc.
\end{itemize}
